### 2020-02-07 ncov_euro.tex
pdf
oops

A novel coronavirus (2019-nCoV) has recently emerged as a global threat.
As the epidemic progresses, many disease modelers have focused on estimating the basic reproductive number \Ro, the average number of secondary cases caused by a primary case in an otherwise susceptible population.
The modeling approaches and resulting estimates of \Ro vary widely, despite relying on similar data sources.

@@

Our results emphasize the importance of propagating uncertainties in all components of \Ro, especially the shape of the generation-interval distribution in efforts to estimate \Ro at the outset of an epidemic.

@@

Basic reproductive number, 2019-nCoV

@@

As the disease continues to spread, many researchers have published their preliminary analyses of the outbreak as pre-prints \cite{bedfordncov, imaincov, liuncov, majumderncov, readncov, zhaoncov}, focusing in particular on estimates of the basic reproductive number \Ro (i.e., the average number of secondary cases generated by a primary case in a fully susceptible population \cite{anderson1991infectious}).
Estimates of the basic reproductive number are of interest during an outbreak because they provide information about the level of intervention required to interrupt transmission, and about the final size of the outbreak \cite{anderson1991infectious}.
We commend these researchers for their timely contribution and those who made the data publicly available.
However, it can be difficult to compare a disparate set of estimates of \Ro from different research groups when the estimation methods and their underlying assumptions vary widely.

>>>>

A novel coronavirus (2019-nCoV) has recently emerged as a global threat.
As the epidemic progresses, many disease modelers have focused on estimating the basic reproductive number \Ro -- the average number of secondary cases caused by a primary case in an otherwise susceptible population.
The modeling approaches and resulting estimates of \Ro vary widely, despite relying on similar data sources.

@@

Our results emphasize the importance of propagating uncertainties in all components of \Ro, including the shape of the generation-interval distribution in efforts to estimate \Ro at the outset of an epidemic.

@@

Basic reproductive number, 2019-nCoV, novel coronavirus, Bayesian multilevel model

@@

As the disease continues to spread, many researchers have published their preliminary analyses of the outbreak as pre-prints \cite{bedfordncov, imaincov, liuncov, majumderncov, readncov, zhaoncov, riouncov}, focusing in particular on estimates of the basic reproductive number \Ro (i.e., the average number of secondary cases generated by a primary case in a fully susceptible population \cite{anderson1991infectious}).
Estimates of the basic reproductive number are of interest during an outbreak because they provide information about the level of intervention required to interrupt transmission, and about the final size of the outbreak \cite{anderson1991infectious}.
We commend these researchers for their timely contribution and those who made the data publicly available.
However, it can be difficult to compare a disparate set of estimates of \Ro from different research groups when the estimation methods and their underlying assumptions vary widely.
